Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2013-12-08 Paper/gammaRays.tex
Added GRObservations c++ code

@@

The burst is fully specified by the following set of parameters:
\begin{itemize}
\item{$v$, the velocity of the shell, $\gamma = \frac{1}{\sqrt{1-v^2}} \gg 1$;}
\item{$\eta_0$, which defines the intensity scale;}
\item{$r_0$, the characteristic jet length; $r_0 \ll \frac{1}{H\left(0\right)}$, $H\left(t\right)$ is the Hubble parameter;}
\item{$n$, which determines the sharpness of the jet end, $n > 3$;}
\item{$\omega_0$, a characteristic radiation frequency;}
\item{$\theta_0$, the opening angle of the jet for radiation with frequency $\omega_0$, $\theta_0 \ll 1$;}
\item{$k$, which determines how much the opening angle changes with frequency, $k < 0$;}
\item{$\alpha$, the bare spectral index, $\alpha < -2k - 1$}
\end{itemize}

@@

\section{Summary}

\bibliographystyle{alpha}
\bibliography{gammaRays}

>>>>

Gamma ray bursts are the most energetic explosions in the Universe, therefore they are of considerable interest for particle physics. Recently developed instruments, specifically Fermi \cite{Ackermann:2012kna} and Swift \cite{SwiftReference} allowed for extensive study of gamma ray bursts \cite{Vianello:2013ela, Gehrels:2013xd}. Many discoveries were made: for example, it was found that the energy emitted by GRBs in gamma rays remains relatively constant for different bursts \cite{Bloom:2003wy}. Temporal variations of GRB spectra were studied. The spectral lags were observed between different low-energy bands \cite{Yi:2005ht}, as well as between low-energy and high energy radiation \cite{}. However, recent observations of luminous bursts by Fermi allowed to study temporal variations even in high energy spectra. In this study we used KS-test to search for spectral lags between two high energy bands: $(\unit[100]{MeV}, \unit[1]{GeV})$ and $(\unit[1]{GeV}, \unit[300]{GeV})$.

@@

The burst is fully specified by the following set of parameters:
\begin{itemize}
\item{$v$, the velocity of the shell, $\gamma = \frac{1}{\sqrt{1-v^2}} \gg 1$.

	If $\gamma$ is small enough, high photon densities would make the jet plasma optically thick to pair production. This in turn would suppress emitted flux, and this is not observed. From this argument the lower bound of $\gamma \ge 100$ was derived \cite{something}. The limited total energy of the burst provides an upper bound: $\gamma \le \gamma_\text{max}$ (see section 3.6). Finally, the model dependent computations of $\gamma$ give the values ranging from $50$ for low-energy bursts to $1000$ for high-energy ones \cite{Ghirlanda:2011ux,Ghisellini:2012nc}. $\gamma$ may vary from burst to burst, and it should decrease during the burst due to the dissipation of energy. As a first approximation we select {\boldmath$\gamma = 100$} for this study.
}
\item{$\eta_0$, which defines the luminosity scale.

	$\eta_0$ controls the number of photons we see from the bursts, and so can be roughly estimated from the number of luminous bursts we observe. We can use this and the measured burst redshifts to estimate both $\eta_0$ and the bursts density $\rho_0$, which will be discussed later. For this study we choose {\boldmath$\eta_0 = 1 \times 10^{45}$}.
}
\item{$r_0$, the characteristic jet length; $r_0 \ll \frac{1}{H\left(0\right)}$, $H\left(t\right)$ is the Hubble parameter;}
\item{$n$, which determines the sharpness of the jet end, $n > 3$;}
\item{$\omega_0$, a characteristic radiation frequency;}
\item{$\theta_0$, the opening angle of the jet for radiation with frequency $\omega_0$, $\theta_0 \ll 1$;}
\item{$k$, which determines how much the opening angle changes with frequency, $k < 0$;}
\item{$\alpha$, the bare spectral index, $\alpha < -2k - 1$}
\end{itemize}

@@

\subsection{Parameter values}

\subsection{Results}

\section{Discussion}

\bibliographystyle{alpha}
\bibliography{/Users/maxitg/Documents/bibliography.bib}
